Causal Distillation Trees

### 2025-03-21 causalDT-manuscript/notebooks/paper_figures.Rmd
add BCF (#2)

COLORS <- c(
  "Distilled Causal Forest" = "#1f5d8f",
  "Distilled Rboost" = "#6aafe4",
  "Virtual Twins" = "#768c50",
  "Causal Tree" = "#953a2f",
  "Linear Regression" = "#b2954a",
  "Lasso" = "#D2BE90"
)
CROSSFIT_COLORS <- c(
  "#981643", "#ED724F", "#F8B06E", "#FCE096", "#8FB989", "#4287B7", "#5E519B"
)
RULEFIT_COLORS <- c(
  "CART" = "#1f5d8f",
  "Rulefit (linear + rules, max depth = 3)" = "#FF9300",
  "Rulefit (linear + rules, max depth = 2)" = "#E7298A",
  "Rulefit (rules only, max depth = 3)" = "#66A61E",
  "Rulefit (rules only, max depth = 2)" = "#7570B3"
)
LINE_TYPES <- c(
  "Pruned" = "solid",
  "Unpruned" = "dashed"
)

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Rboost",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

@@

    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
  height = 9.5, 
  width = 15
)

@@

    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.08, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
  height = 9.5, 
  width = 15
)
```

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Causal Tree",
  "Causal Tree (unpruned)"
)

@@

    if (sim_name != sim_names[length(sim_names)]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[6] ~ 0.6,
      TRUE ~ 0.5
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features\n(max depth = 2)"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds\n(max depth = 2)"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs\n(max depth = 2)"
        )
    }
    if (stringr::str_detect(sim_name, "with")) {
      tag_x_pos <- -.08
    } else {
      tag_x_pos <- -.03
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(tag_x_pos, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[length(sim_names)]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.95, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_max_depth2.pdf"),
  height = 17, 
  width = 14
)
```

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Rboost",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Rboost",
  "Causal Tree"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

@@

plt <- purrr::map(
  sim_names,
  function(sim_name) {
    f1_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "F1"
      ) |> 
      dplyr::mutate(
        .value = mean_feature_selection_err
      )
    cate_df <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "rmse"
      ) |> 
      dplyr::mutate(
        .metric = "Subgroup ATE RMSE",
        .value = mean_ate_err
      )

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Virtual Twins",
  "Causal Tree",
  "Causal Tree (unpruned)",
  "Linear Regression",
  "Lasso"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

# without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::imap(
  sim_names,
  function(sim_name, idx) {
    tag <- LETTERS[idx]
    plt <- viz_results_ls[[sim_name]]$`Feature and Split Frequency Plots`[[1]]
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      )
    plt <- plt +
      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        )
      )
    if (stringr::str_detect(sim_name, "with")) {
      plt <- plt + 
        ggplot2::labs(y = "")
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 2, guides = "collect", byrow = FALSE
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_ntrees.pdf"),
  height = 15.5, 
  width = 13
)
```

>>>>

COLORS <- c(
  "Distilled Rboost" = "#6aafe4",
  "Distilled Causal Forest" = "#1f5d8f",
  "Distilled BCF" = "#1c3145",
  "Virtual Twins" = "#768c50",
  "Causal Tree" = "#953a2f",
  "Linear Regression" = "#b2954a",
  "Lasso" = "#D2BE90"
)
CROSSFIT_COLORS <- c(
  "#981643", "#ED724F", "#F8B06E", "#FCE096", "#8FB989", "#4287B7", "#5E519B"
)
RULEFIT_COLORS <- c(
  "CART" = "#1f5d8f",
  "Rulefit (linear + rules, max depth = 3)" = "#FF9300",
  "Rulefit (linear + rules, max depth = 2)" = "#E7298A",
  "Rulefit (rules only, max depth = 3)" = "#66A61E",
  "Rulefit (rules only, max depth = 2)" = "#7570B3"
)
LINE_TYPES <- c(
  "Pruned" = "solid",
  "Unpruned" = "dashed"
)

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

@@

    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
  height = 9.5, 
  width = 15
)

@@

    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.08, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
  height = 9.5, 
  width = 15
)
```

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled BCF",
  "Distilled BCF (unpruned)",
  "Causal Tree",
  "Causal Tree (unpruned)"
)

@@

    if (sim_name != sim_names[length(sim_names)]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none", linetype = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[6] ~ 0.6,
      TRUE ~ 0.5
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features\n(max depth = 2)"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds\n(max depth = 2)"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs\n(max depth = 2)"
        )
    }
    if (stringr::str_detect(sim_name, "with")) {
      tag_x_pos <- -.08
    } else {
      tag_x_pos <- -.03
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(tag_x_pos, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[length(sim_names)]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.95, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_max_depth2.pdf"),
  height = 17, 
  width = 14
)
```

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Causal Forest",
  "Distilled BCF",
  "Causal Tree"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

@@

plt <- purrr::map(
  sim_names,
  function(sim_name) {
    f1_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "F1"
      ) |> 
      dplyr::mutate(
        .value = mean_feature_selection_err
      )
    cate_df <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY,
        .metric == "rmse"
      ) |> 
      dplyr::mutate(
        .metric = "Subgroup\nATE RMSE",
        .value = mean_ate_err
      )

@@

```{r}
KEEP_METHODS <- c(
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled BCF",
  "Distilled BCF (unpruned)",
  "Virtual Twins",
  "Causal Tree",
  "Causal Tree (unpruned)",
  "Linear Regression",
  "Lasso"
)
KEEP_HERITABILITY <- c(0.2, 0.6, 1)

# without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::imap(
  sim_names,
  function(sim_name, idx) {
    tag <- LETTERS[idx]
    plt <- viz_results_ls[[sim_name]]$`Feature and Split Frequency Plots`[[1]]
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        tau_heritability %in% KEEP_HERITABILITY
      )
    plt <- plt +
      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        )
      )
    if (stringr::str_detect(sim_name, "with")) {
      plt <- plt + 
        ggplot2::labs(y = "")
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 2, guides = "collect", byrow = FALSE
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_ntrees.pdf"),
  height = 18, 
  width = 13
)
```
